\nonstopmode{}
\documentclass[letterpaper]{book}
\usepackage[times,inconsolata,hyper]{Rd}
\usepackage{makeidx}
\usepackage[utf8]{inputenc} % @SET ENCODING@
% \usepackage{graphicx} % @USE GRAPHICX@
\makeindex{}
\begin{document}
\chapter*{}
\begin{center}
{\textbf{\huge Package `Bundesliga'}}
\par\bigskip{\large \today}
\end{center}
\inputencoding{utf8}
\ifthenelse{\boolean{Rd@use@hyper}}{\hypersetup{pdftitle = {Bundesliga: Analytical Functions And Data Around European Football Leagues}}}{}
\ifthenelse{\boolean{Rd@use@hyper}}{\hypersetup{pdfauthor = {Len Bauer}}}{}
\begin{description}
\raggedright{}
\item[Title]\AsIs{Analytical Functions And Data Around European Football Leagues}
\item[Version]\AsIs{1.0}
\item[Description]\AsIs{This package provides data to market values and rankings of the last periods of the european football leagues. Functions to analyse their connectivity threw an ... test are provided.}
\item[License]\AsIs{MIT + file LICENSE}
\item[Encoding]\AsIs{UTF-8}
\item[Roxygen]\AsIs{list(markdown = TRUE)}
\item[RoxygenNote]\AsIs{7.2.3}
\item[Suggests]\AsIs{testthat (>= 3.0.0)}
\item[Config/testthat/edition]\AsIs{3}
\item[NeedsCompilation]\AsIs{no}
\item[Author]\AsIs{Len Bauer [aut, cre] (<}\url{https://orcid.org/0000-0002-2822-4802}\AsIs{>)}
\item[Maintainer]\AsIs{Len Bauer }\email{lh.bauer18@gmail.com}\AsIs{}
\end{description}
\Rdcontents{\R{} topics documented:}
\inputencoding{utf8}
\HeaderA{filter\_data}{filter\_data}{filter.Rul.data}
%
\begin{Description}\relax
Filter data by parameter. You have to put in at least the season you want to start extracting data and one team or league you want to gather data from!
\end{Description}
%
\begin{Usage}
\begin{verbatim}
filter_data(
  data,
  saison_von,
  saison_bis = 2022,
  teams = "ALLTEAMS",
  ligen = "ALLLEAGUES",
  platzierungen = "ALLPLACES",
  punkte = "ALLPOINTS",
  marktwert_von = "ALLVALUESFROM",
  marktwert_bis = "ALLVALUESTO"
)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{data}] database you are looking through

\item[\code{saison\_von}] The first season from which you want to extract the data. If you want to extract data from the 2018/19 season set 'saison\_von = 2018'.

\item[\code{saison\_bis}] The last season from which you want to extract the data. It's set to 2023 /the actual year by default.
If you want to extract data from the 2021/22 season set 'saison\_bis = 2021'.

\item[\code{teams}] A character-vector with the teams you're searching for. optional

\item[\code{ligen}] A character-vector with the leagues you're searching for. optional

\item[\code{platzierungen}] A integer-vector with the end-season-placements optional

\item[\code{punkte}] A integer-vector with the points you're searching for. optional

\item[\code{marktwert\_von}] A integer with the min-marketvalue you're searching for.

\item[\code{marktwert\_bis}] A integer with the max-marketvalue you're searching for. optional
\end{ldescription}
\end{Arguments}
%
\begin{Value}
database
\end{Value}
%
\begin{Examples}
\begin{ExampleCode}
this is not an example
\end{ExampleCode}
\end{Examples}
\printindex{}
\end{document}
